Locus Statistics

### 2017-08-17 doc/RMD/locus-stats.Rmd
Add repeat motif to locus table stats
I also removed the average values because it only
made sense for three of the numbers. Now all but
table 1 are reproducible.

```{r locus_table, comment = NA}
makerange <- . %>% as.integer() %>% range() %>% paste(collapse = "-")

ranges <- map_chr(alleles(dat11), makerange)
ranges <- c(ranges, alleles(dat11) %>% unlist(use.names = FALSE) %>% makerange)
locus_table(dat11, information = FALSE) %>% 
  as.data.frame() %>%
  rownames_to_column("Locus") %>%
  mutate(Locus = gsub("\\([FH]\\)", "", Locus)) %>%
  add_column(Range = ranges) %>%
  select(Locus, Range, allele, Hexp, Evenness) %>%
  mutate(allele = round(allele, 2)) %>%
  rename(`*h*` = Hexp, `No. alleles` = allele) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(1:12, 3, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 4:5, 2) %>%
  huxtable::set_align(huxtable::everywhere, 3:5, "right") %>%
  huxtable::set_col_width(c(0.06, 0.07, 0.12, 0.06, 0.09)) %>%
  huxtable::print_md(max_width = 47)
```

>>>>

```{r locus_table, comment = NA}
makerange <- . %>% as.integer() %>% range() %>% paste(collapse = "--")

ranges <- map_chr(alleles(dat11), makerange)
# ranges <- c(ranges, alleles(dat11) %>% unlist(use.names = FALSE) %>% makerange)
locus_table(dat11, information = FALSE) %>% 
  as.data.frame() %>%
  rownames_to_column("Locus") %>%
  slice(-n()) %>%
  mutate(Locus = gsub("\\([FH]\\)", "", Locus)) %>%
  add_column(Range = ranges) %>%
  add_column(Repeats = other(dat11)$REPLEN[locNames(dat11)]) %>%
  select(Locus, Range, Repeats, allele, Hexp, Evenness) %>%
  readr::write_csv(file.path(PROJHOME, "results/tables/locus-table.csv"), col_names = TRUE) %>%
  mutate(allele = round(allele, 2)) %>%
  mutate(Repeats = case_when(
    Repeats <= 2 ~ "di-",
    Repeats <= 3 ~ "tri-",
    Repeats <= 4 ~ "tetra-",
    Repeats <= 5 ~ "penta-",
    Repeats <= 6 ~ "hexa-"
  )) %>%
  rename(`*h*` = Hexp) %>%
  rename(`No. alleles` = allele) %>%
  rename(`Repeat Motif` = Repeats) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 3:4, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 5:6, 2) %>%
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>%
  huxtable::set_col_width(c(0.06, 0.07, 0.11, 0.1, 0.05, 0.075)) %>%
  huxtable::print_md(max_width = 61)
```
